Computational musicology, ????, Profit

### 2016-07-23 paper.tex
s/Algomusicology/Computational musicology/g

\title{Algomusicology, ????, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
In this paper I propose a novel method for converting algomusicology into profit. While my particular example
is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
traditional notions of musical authorship.
\end{abstract}

@@

Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
which is a portmanteau of algorithm and musicology similar to algorave, to describe the use of information theory and programming for musical analysis.}

@@

On one level, the puzzle posed by the title of this paper has a straightforward solution:
\begin{enumerate}
    \item Algomusicology
    \item Copyright litigation
    \item Profit!
\end{enumerate}

More seriously, this paper attempts to show that algomusicology can meaningfully shed light on how music works. Also, as in
the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
In other words, algomusicology can contribute to musical practice, not just explain it.

@@

Algomusicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
significance give algomusicology great potential as a source of artistic analysis and inspiration.

>>>>

\title{Computational musicology, ????, Profit}
%\subtitle{Subtitle Text, if any}

@@

\begin{abstract}
In this paper I propose a novel method for converting computational musicology into profit. While my particular example
is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
traditional notions of musical authorship.
\end{abstract}

@@

Less glibly, is computational musicology doomed to be a mere observer and explainer of musical practice, or might it become an
active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
Can computational musicology influence music?

@@

On one level, the puzzle posed by the title of this paper has a straightforward solution:
\begin{enumerate}
    \item Computational musicology
    \item Copyright litigation
    \item Profit!
\end{enumerate}

More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music works. Also, as in
the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
In other words, computational musicology can contribute to musical practice, not just explain it.

@@

Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
significance give computational musicology great potential as a source of artistic analysis and inspiration.
